Happiness Does Not Cause Altruism: A review of US General Social Survey data

### 2023-03-17 outputs/paper/paper.qmd
Updates to paper – survey

### Appendix A: Supplementary Survey
Researchers have long sought to find a connection between happiness and altruistic actions. Some studies show that happiness may lead to greater levels of altruism, while others fail to find a relationship between the emotion and subsequent action. With homelessness on the rise and a growing separation between socio-economic classes, it is important to discover the leading causes of altruism.

@@

1.  On a scale of 1-5, how happy do you feel right now?
    a. Very happy
    b. Pretty happy
    c. Happy
    d. Not too happy
    e. Unhappy
2.  How often have you given directions to a stranger in the past year?
    a. More than once a week
    b. Once a week
    c. Once a month 
    d. At least 2 or 3 times in the past year
    e. Once in the past year
    f. Not at all in the past year
3.  How often are you given the opportunity to give directions to a stranger?
    a. More than once a week
    b. Once a week
    c. Once a month 
    d. At least 2 or 3 times in the past year
    e. Once in the past year
    f. Not at all in the past year
4.  If did not give directions to a stranger, did you want to?
    a. Yes
    b. It depends on the day
    c. It depends on the time I have in the moment
    d. No
5.  If you had the desire but did not give directions to a stranger, what prevented you from doing so?
    a. I do not live in an area with a lot of strangers asking for directions
    b. I did not have the time to help
    c. I did not know enough about the area to be helpful
    d. Another factor beyond my control prevented me from helping
6.  How often have you donated food or money to a homeless person in the past year?
    a. More than once a week
    b. Once a week
    c. Once a month 
    d. At least 2 or 3 times in the past year
    e. Once in the past year
    f. Not at all in the past year
7.  How often are you given the opportunity to donate to a homeless person?
    a. More than once a week
    b. Once a week
    c. Once a month 
    d. At least 2 or 3 times in the past year
    e. Once in the past year
    f. Not at all in the past year
8.  If did not donate to a homeless person, did you want to?
    a. Yes
    b. It depends on the day
    c. It depends on the money and resources at my disposal
    d. No
9.  If you had the desire but did not donate to a homeless person, what prevented you from doing so?
    a. I do not live in an area with a lot of homeless people
    b. I did not have the time to help
    c. I did not have the money or resources to help
    d. Another factor beyond my control prevented me from helping

Thank you for participating in this survey! Your responses will greatly aid our effort to understand altruism and whether happiness has any impact on the behavior. If at any time you wish to withdraw from this survey, please contact Sebastian Rodriguez (s [dot] rodriguez [at] mail [dot] utoronto [dot] ca).

>>>>

### Appendix A: Supplementary Survey
The supplementary survey attached to this project is available through Google Forms: https://forms.gle/Zr2jj93bXFaaPkPdA.

#### Survey Introduction 
Researchers have long sought to find a connection between happiness and altruistic actions. Some studies show that happiness may lead to greater levels of altruism, while others fail to find a relationship between the emotion and subsequent action. With homelessness on the rise and a growing separation between socio-economic classes, it is important to discover the leading causes of altruism.

@@

#### Survey Questions
1.  On a scale of 1-5, how happy do you feel right now?
    a. Very happy
    b. Pretty happy
    c. Happy
    d. Not too happy
    e. Unhappy
2.  How often have you given directions to a stranger in the past year?
    a. More than once a week
    b. Once a week
    c. Once a month 
    d. At least 2 or 3 times in the past year
    e. Once in the past year
    f. Not at all in the past year
3.  How often are you given the opportunity to give directions to a stranger?
    a. More than once a week
    b. Once a week
    c. Once a month 
    d. At least 2 or 3 times in the past year
    e. Once in the past year
    f. Not at all in the past year
4.  If you did not give directions to a stranger, did you want to?
    a. Yes
    b. It depends on the day
    c. It depends on the time I have in the moment
    d. No
5.  If you had the desire but did not give directions to a stranger, what prevented you from doing so?
    a. I do not live in an area with a lot of strangers asking for directions
    b. I did not have the time to help
    c. I did not know enough about the area to be helpful
    d. Another factor beyond my control prevented me from helping
6.  How often have you donated food or money to a homeless person in the past year?
    a. More than once a week
    b. Once a week
    c. Once a month 
    d. At least 2 or 3 times in the past year
    e. Once in the past year
    f. Not at all in the past year
7.  How often are you given the opportunity to donate to a homeless person?
    a. More than once a week
    b. Once a week
    c. Once a month 
    d. At least 2 or 3 times in the past year
    e. Once in the past year
    f. Not at all in the past year
8.  If you did not donate to a homeless person, did you want to?
    a. Yes
    b. It depends on the day
    c. It depends on the money and resources at my disposal
    d. No
9.  If you had the desire but did not donate to a homeless person, what prevented you from doing so?
    a. I do not live in an area with a lot of homeless people
    b. I did not have the time to help
    c. I did not have the money or resources to help
    d. Another factor beyond my control prevented me from helping

#### Survey Conclusion
Thank you for participating in this survey! Your responses will greatly aid our effort to understand altruism and whether happiness has any impact on the behavior. If at any time you wish to withdraw from this survey, please contact Sebastian Rodriguez (s [dot] rodriguez [at] mail [dot] utoronto [dot] ca).
